Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-04-14 public/paper/pyg4ometry.tex
Removed generic as only different constructors

\begin{table}[hbt!]
\centering
\begin{tabular}{ l l l } \hline
GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
Define 			& Constant				& gdml.Constant				\\
				& Variable					& gdml.Variable					\\
				& Quantity					& gdml.Quantity				\\
				& Expression 				& gdml.Expression				\\
				& Position					& gdml.Position					\\
				& Rotation					& gdml.Rotation				\\
				& Scale					& gdml.Scale					\\
				& Matrix					& gdml.Matrix					\\ \hline
Materials 			& Element					& geant4.Element				\\
				& Isotope					& geant4.Isotope				\\
				& Material					& geant4.Material				\\ \hline
Solid  			& Box					& geant4.solid.Box				\\
	  			& Tube					& geant4.solid.Tubs				\\
	  			& CutTube				& geant4.solid.CutTubs			\\
	  			& Cone					& geant4.solid.Cons				\\
	  			& Para					& geant4.solid.Para				\\
	  			& Trd					& geant4.solid.Trd				\\
	  			& Trap					& geant4.solid.Trap				\\
	  			& Sphere					& geant4.solid.Sphere			\\
	  			& Orb					& geant4.solid.Orb				\\
	  			& Torus					& geant4.solid.Torus				\\
	  			& Polycone				& geant4.solid.Polycone			\\
	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
	  			& Polyhedra				& geant4.solid.Polyhedra			\\
	  			& Eltube					& geant4.solid.EllipticalTube		\\
	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
	  			& Elcone					& geant4.solid.EllipticalCone		\\
				& Paraboloid				& geant4.solid.Paraboloid			\\
				& Hype					& geant4.solid.Hyperboloid		\\
				& Tet						& geant4.solid.Tet				\\
				& Xtru					& geant4.solid.ExtrudedSolid		\\
				& TwistedBox				& geant4.solid.TwistedBox		\\
				& TwistedTtap				& geant4.solid.TwistedTrap		\\
				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
				& TwistedTube				& geant4.solid.TwistedTube		\\
				& Arb8					& geant4.solid.GenericTrap		\\
				& Tessellated				& geant4.solid.TessellatedSolid 	\\
				& Union					& geant4.solid.Union				\\
				& Subtraction				& geant4.solid.Subtraction			\\
				& Intersection				& geant4.solid.Intersection 		\\
				& MultiUnion				& geant4.solid.MultiUnion 			\\
				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
Structure			& Volume					& geant4.LogicalVolume			\\
				& Assembly				& geant4.AssemblyVolume 		\\
				& PhysVol					& geant4.PhysicalVolume			\\ 
				& ReplicaVol				& geant4.ReplicaVolume			\\ 
				& ParaVol					& geant4.ParameterisedVolume	\\ 
				& DivisionVol				& geant4.DivisionVolume			\\
				& SkinSurface				& geant4.SkinSurface			\\ 
				& BorderSurface			& geant4.BorderSurface			\\ \hline

@@

\begin{table}[hbt!]
\centering
\begin{tabular}{ l  l  } \hline
Geant4 solid			& FLUKA region constuction		\\ \hline
Box					& +2 XYP + 2 XZP + 2 YZP 		\\
Tube					& +ZCC - 2 PLA -2 XYP - ZCC	 	\\
CutTube				& +ZCC - 4 PLA -ZCC			\\
Cone				& +TRC - TRC - 2 PLA 			\\
Para					& + 6 PLA						\\
Trd					& + 6 PLA						\\
Trap					& + 6 PLA						\\
Sphere				& +SPH - SPH  - 2 PLA - 2 TRC	\\
Orb					& +SPH						\\
Torus				& +$N$ ZCC  - $N$ PLA			\\
Polycone				& +$N$ TRC -2 PLA				\\
GenericPolycone		& +$N$ ARB					\\
Polyhedra				& +$N$ PLA					\\
Eltube				& +ZEC  - 2 XYP				\\
Ellipsoid				& +ELL - 2 XYP		 			\\
Elcone				& +QUA - 2 XYP				\\
Paraboloid			& +QUA - 2 XYP				\\
Hype					& +QUA - QUA - 2 XYP			\\
Tet					& +4 PLA						\\
Xtru					& +$N_{\rm plane} N_{\rm point}$ PLA \\
TwistedBox			& +$N$ PLA					\\
TwistedTtap			& +$N$ PLA					\\
TwistedTrd			& +$N$ PLA				 	\\
TwistedTube			& +$N$ PLA					\\
Arb8					& +$N$ PLA					\\
Tessellated			& +$N$ PLA				 	\\
Union				& $R_1 \cup R_2$				\\
Subtraction			& $R_1 - R_2$					\\
Intersection			& $R_1 \cap R_2$				\\
MultiUnion			& $R_1 \cup R_2 \cup R_3 \cup$	\\ \hline
\end{tabular}
\label{tab:geant2fluka}
\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
\end{table}

@@

\subsection{TODO}
\begin{itemize}
\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
\item Scaled solid 
\item Placement scale 
\item Replica, Division, Parameterised
\item Materials 
\end{itemize}

>>>>

\begin{table}[hbt!]
\centering
\begin{tabular}{ l l l } \hline
GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
Define 			& Constant				& gdml.Constant				\\
				& Variable					& gdml.Variable					\\
				& Quantity					& gdml.Quantity				\\
				& Expression 				& gdml.Expression				\\
				& Position					& gdml.Position					\\
				& Rotation					& gdml.Rotation				\\
				& Scale					& gdml.Scale					\\
				& Matrix					& gdml.Matrix					\\ \hline
Materials 			& Element					& geant4.Element				\\
				& Isotope					& geant4.Isotope				\\
				& Material					& geant4.Material				\\ \hline
Solid  			& Box					& geant4.solid.Box				\\
	  			& Tube					& geant4.solid.Tubs				\\
	  			& CutTube				& geant4.solid.CutTubs			\\
	  			& Cone					& geant4.solid.Cons				\\
	  			& Para					& geant4.solid.Para				\\
	  			& Trd					& geant4.solid.Trd				\\
	  			& Trap					& geant4.solid.Trap				\\
	  			& Sphere					& geant4.solid.Sphere			\\
	  			& Orb					& geant4.solid.Orb				\\
	  			& Torus					& geant4.solid.Torus				\\
	  			& Polycone				& geant4.solid.Polycone			\\
	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
	  			& Polyhedra				& geant4.solid.Polyhedra			\\
				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
	  			& Eltube					& geant4.solid.EllipticalTube		\\
	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
	  			& Elcone					& geant4.solid.EllipticalCone		\\
				& Paraboloid				& geant4.solid.Paraboloid			\\
				& Hype					& geant4.solid.Hyperboloid		\\
				& Tet						& geant4.solid.Tet				\\
				& Xtru					& geant4.solid.ExtrudedSolid		\\
				& TwistedBox				& geant4.solid.TwistedBox		\\
				& TwistedTtap				& geant4.solid.TwistedTrap		\\
				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
				& TwistedTube				& geant4.solid.TwistedTube		\\
				& Arb8					& geant4.solid.GenericTrap		\\
				& Tessellated				& geant4.solid.TessellatedSolid 	\\
				& Union					& geant4.solid.Union				\\
				& Subtraction				& geant4.solid.Subtraction			\\
				& Intersection				& geant4.solid.Intersection 		\\
				& MultiUnion				& geant4.solid.MultiUnion 			\\
				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
Structure			& Volume					& geant4.LogicalVolume			\\
				& Assembly				& geant4.AssemblyVolume 		\\
				& PhysVol					& geant4.PhysicalVolume			\\ 
				& ReplicaVol				& geant4.ReplicaVolume			\\ 
				& ParaVol					& geant4.ParameterisedVolume	\\ 
				& DivisionVol				& geant4.DivisionVolume			\\
				& SkinSurface				& geant4.SkinSurface			\\ 
				& BorderSurface			& geant4.BorderSurface			\\ \hline

@@

\begin{table}[hbt!]
\centering
\begin{tabular}{ l  l  } \hline
Geant4 solid			& FLUKA region constuction		\\ \hline
Box					& +2 XYP + 2 XZP + 2 YZP 		\\
Tube					& +ZCC - 2 PLA -2 XYP - ZCC	 	\\
CutTube				& +ZCC - 4 PLA -ZCC			\\
Cone				& +TRC - TRC - 2 PLA 			\\
Para					& + 6 PLA						\\
Trd					& + 6 PLA						\\
Trap					& + 6 PLA						\\
Sphere				& +SPH - SPH  - 2 PLA - 2 TRC	\\
Orb					& +SPH						\\
Torus				& +$N$ ZCC  - $N$ PLA			\\
Polycone				& +$N$ TRC -2 PLA				\\
Polyhedra				& +$N$ PLA					\\
Eltube				& +ZEC  - 2 XYP				\\
Ellipsoid				& +ELL - 2 XYP		 			\\
Elcone				& +QUA - 2 XYP				\\
Paraboloid			& +QUA - 2 XYP				\\
Hype					& +QUA - QUA - 2 XYP			\\
Tet					& +4 PLA						\\
Xtru					& +$N_{\rm plane} N_{\rm point}$ PLA \\
TwistedBox			& +$N$ PLA					\\
TwistedTtap			& +$N$ PLA					\\
TwistedTrd			& +$N$ PLA				 	\\
TwistedTube			& +$N$ PLA					\\
Arb8					& +$N$ PLA					\\
Tessellated			& +$N$ PLA				 	\\
Union				& $R_1 \cup R_2$				\\
Subtraction			& $R_1 - R_2$					\\
Intersection			& $R_1 \cap R_2$				\\
MultiUnion			& $R_1 \cup R_2 \cup R_3 \cup$	\\ \hline
\end{tabular}
\label{tab:geant2fluka}
\caption{GDML/Geant4 solids and the mapping to FLUKA bodies}
\end{table}

@@

\subsection{TODO}
\begin{itemize}
\item Non-convex solids, convex decomposition (Polyhedron, Xtru, TwistedBox, TwistedTrap, TwistedTrd, TwistedTube)
\item Non-convex 2D section (GenericPolycone, GenericPolyhedra)
\item Scaled solid 
\item Placement scale 
\item Replica, Division, Parameterised
\item Materials 
\end{itemize}
